---
title: "Lottery Helper"
author: "Tyler Beason"
#date: "Sunday, February 01, 2015"
runtime: shiny
output: html_document
---

##This guide can help you choose *your* lottery numbers to snatch those **big payouts**.  
<br>
The last numbers drawn were
```{r, echo=FALSE}
numberData <- reactiveFileReader(1000,NULL,"http://www.ialottery.com/Results/power.txt",read.delim,stringsAsFactors=FALSE)
renderTable({
  head(numberData(),1)
})

```

Perhaps those weren't your numbers? Sorry to hear that. Use the app below to improve your odds next time!

First, how likely were those numbers?

```{r,echo=FALSE}
renderPrint({
  data <-numberData()
  prob <- function(n){
    counter <- length(which(data[2:nrow(data),n+1]==data[1,n+1]))
    counter/(nrow(data)-1)
  }
  cat("First number was", data[1,2],"which is drawn first", format(prob(1)*100,digits=2),"% of the time.\n")
  cat("Second number was", data[1,3],"which is drawn second", format(prob(2)*100,digits=2),"% of the time.\n")
  cat("Third number was", data[1,4],"which is drawn third", format(prob(3)*100,digits=2),"% of the time.\n")
  cat("Fourth number was", data[1,5],"which is drawn fourth", format(prob(4)*100,digits=2),"% of the time.\n")
  cat("Fifth number was", data[1,6],"which is drawn fifth", format(prob(5)*100,digits=2),"% of the time.\n")
  cat("Powerball number was", data[1,7],"which is drawn", format(prob(6)*100,digits=2),"% of the time.\n")
  
})

```


```{r, echo=FALSE}
selectInput("col","Select draw number:",
            c("1"=1,"2"=2,"3"=3,"4"=4,"5"=5,"Powerball"=6))
renderPlot({
  data <- numberData()
  hist(data[,as.numeric(input$col)+1],main=paste("Histogram of draw number ", as.numeric(input$col)),xlab="Number",breaks=16)
})
renderPrint({
  data <- numberData()
  summary(data[,as.numeric(input$col)+1])
})
renderPlot({
  data <- numberData()
  sums <- rowSums(data[,2:6])
  plot(sums,main="Sums of first 5 numbers for every drawing",xlab=NA,ylab="Sum")
})
```

```{r, echo=FALSE}

numericInput("num", "Input a number:",min=1,max=59,value=1)
```

The number `r renderText({input$num})` has been drawn a total of `r renderText({
data <- numberData()
length(which(data[,2:6]==input$num))})` times. It has been the Powerball `r renderText({
data <- numberData()
length(which(data[,7]==input$num))})` times. It was most recently drawn on `r renderText({
data <- numberData()
ind <- which(data[,2:7]==input$num)[[1]]
data[ind,1]})`.

<br>
*Disclaimer: The Powerball lottery rules have changed over time, and this data may not reflect actual rules over all periods. See http://www.powerball.com for official rules. Using this app does not guarantee winnings, but the author would happily accept any donations if the app helps you win. If you are addicted to gambling (which includes purchasing lottery tickets), know that it is almost impossibly unlikely that you'll ever win and you should find something more productive to be addicted to.*  
Lottery Results from: http://www.ialottery.com